---
title: Post
author: Crystal
date: '2019-04-26'
slug: rplot
categories:
  - blog
  - R
tags:
  - plot
  - R Markdown
description: ''
externalLink: ''
series: []
---

This post combines two part: one is story part, the other one is plot part:

Story Part:

There was a farmer who sold a pound of butter to a baker.One day the baker decided to weigh the
butter to see if he was getting the right amount, which he wasn’t. Angry about this, he took the
farmer to court.

The judge asked the farmer if he was using any measure to weight the butter. The farmer replied,
“Honor, I am primitive. I don’t have a proper measure, but I do have a scale.”The judge asked,
“Then how do you weigh the butter?”

The farmer replied; “YOUR HONOR, LONG BEFORE THE BAKER STARTED BUYING BUTTER FROM ME, I HAVE
BEEN BUYING A POUND LOAF OF BREAD FROM HIM. EVERY DAY WHEN THE BAKER BRINGS THE BREAD, I PUT IT
ON THE SCALE AND GIVE HIM THE SAME WEIGHT IN BUTTER. IF ANYONE IS TO BE BLAMED, IT IS THE
BAKER.”

Second one: 

One warm evening many years ago…

After spending nearly every waking minute with Angel for eight straight days, I knew that I had
to tell her just one thing.  So late at night, just before she fell asleep, I whispered it in
her ear.  She smiled – the kind of smile that makes me smile back –and she said, “When I’m
seventy-five and I think about my life and what it was like to be young, I hope that I can
remember this very moment.”

A few seconds later she closed her eyes and fell asleep. The room was peaceful – almost silent.
All I could hear was the soft purr of her breathing.

I stayed awake thinking about the time we’d spent together and all the choices in our lives that
made this moment possible.  And at some point, I realized that it didn’t matter what we’d done
or where we’d gone.  Nor did the future hold any significance.

All that mattered was the serenity of the moment.
Just being with her and breathing with her.

Plotly Part Exercise: 

```{r interactive, message=FALSE}
#devtools::install_github("tidyverse/ggplot2")
#install.packages("ggrepel")
library(plotly)
library(ggrepel)

mtcars$label <- rownames(mtcars)
mtcars$label[mtcars$cyl != 6] <- ""

# New! (not available in ggplot2 version 2.2.1 or earlier)
pos <- position_jitter(width = 0.3, seed = 2)


my_cool_plot<- ggplot(mtcars, aes(factor(cyl), mpg, label=rownames(mtcars) , color=cyl)) +
  geom_point(position = pos) +
  geom_text_repel(position = pos) +
  theme(legend.position = "none") +
  labs(title = "position_jitter()")
#
my_cool_plot
# 
ggplotly(my_cool_plot)

```



```{r ggextension-examples}
#library(ggplot2)
#install.packages("viridisLite")
# Example for `geom_ridgeline_gradient()`
library(viridis)
library(viridisLite)
library(ggridges)
#install.packages("viridis")
#library(ggplot2)

d <- data.frame(x = rep(1:5, 3) + c(rep(0, 5), rep(0.3, 5), rep(0.6, 5)),
                y = c(rep(0, 5), rep(1, 5), rep(3, 5)),
                height = c(0, 1, 3, 4, 0, 1, 2, 3, 5, 4, 0, 5, 4, 4, 1))

ggplot(d, aes(x, y, height = height, group=y, fill = factor(x+y))) +
  geom_ridgeline_gradient() +
  scale_fill_viridis(discrete = TRUE, direction = -1, guide = "none")

```


```{r lincoln_weather example}

ggplot(lincoln_weather, aes(x = `Mean Temperature [F]`, y = `Month`, fill = ..x..)) +
  geom_density_ridges_gradient(scale = 3, rel_min_height = 0.01) +
  scale_fill_viridis(name = "Temp. [F]", option = "C") +
  labs(title = 'Temperatures in Lincoln NE in 2016')
```